The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
new asteroseismic figure

\begin{figure*}
\noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}

\caption{\label{masses}
Using asteroseismic constraints (left) and asteroseismic and spectroscopic constraints jointly (right) we infer the masses of each star in the asteroseismic sample of giants.}
\end{figure*}

>>>>

\begin{figure}
% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{different_constraints_ben.pdf}

\caption{\label{masses}
Using asteroseismic constraints only (red) and asteroseismic and spectroscopic constraints jointly (blue) we infer the masses of each star in the asteroseismic sample of giants.}
\end{figure}
